\section{Installation}\label{sec:install}
Everywhere in the below text it is assumed that the root directory of this software is
\codet{<OWON\textunderscore DIR>}.

\subsection{Stand-alone}
In order to install the library you should compile dynamic library (shared object) and
place it in standard location (\codet{/usr/lib/} in this case). The instructions are the
following:
\begin{lstlisting}[language=bash]
cd <OWON_DIR>/make
make compile
sudo make link 
make clean
\end{lstlisting}

Also it is useful to extend the standart include path with the path to the headers. It
allows you, for example, not use the include option (\codet{-I}) while compiling. Place
the following lines in your \codet{.profile}, or \codet{.bash\tus profile} if that is
what you have.
\begin{lstlisting}[language=bash]
if [[ -n "$CPLUS_INCLUDE_PATH" ]]; then
    CPLUS_INCLUDE_PATH=$CPLUS_INCLUDE_PATH:/path/to/<OWON_DIR>/inc
else
    export CPLUS_INCLUDE_PATH=/path/to/<OWON_DIR>/inc
fi;
\end{lstlisting}
where \codet{/path/to/<OWON\tus DIR>} is the absolute path to the \codet{<OWON\tus DIR>}.

Now logout and login back. That's all!

\subsection{ROOT-compatible}\label{ssec:install:ROOT}
Read this section only if you intend to use ROOT CERN framework to create \codet{TTree}s
from several binary file. For more details, see Sec.~\ref{ssec:ROOT}.
At this stage you need to install Boost Filesystem Library on your system. Of course, ROOT should be installed also.

After all the prerequisites are installed the final step is to compile everything in `.so` object:
\begin{lstlisting}[language=bash]
cd <OWON_DIR>/make
root -l CompileROOT.C
\end{lstlisting}
